---
title: "Machine Learning Fundamentals"
author: "Danny Jordan"
---



# Challenge Summary

__Your organization wants to know which companies are similar to each other to help in identifying potential customers of a SAAS software solution (e.g. Salesforce CRM or equivalent) in various segments of the market. The Sales Department is very interested in this analysis, which will help them more easily penetrate various market segments.__

You will be using stock prices in this analysis. You come up with a method to classify companies based on how their stocks trade using their daily stock returns (percentage movement from one day to the next). This analysis will help your organization determine which companies are related to each other (competitors and have similar attributes). 

You can analyze the stock prices using what you've learned in the unsupervised learning tools including K-Means and UMAP. You will use a combination of `kmeans()` to find groups and `umap()` to visualize similarity of daily stock returns.

# Objectives

Apply your knowledge on K-Means and UMAP along with `dplyr`, `ggplot2`, and `purrr` to create a visualization that identifies subgroups in the S&P 500 Index. You will specifically apply:

- Modeling: `kmeans()` and `umap()`
- Iteration: `purrr`
- Data Manipulation: `dplyr`, `tidyr`, and `tibble`
- Visualization: `ggplot2` (bonus `plotly`)


# Libraries

Load the following libraries. 

```{r}
# install.packages("plotly")

library(tidyverse)
library(tidyquant)
library(broom)
library(umap)

library(magrittr)
library(dplyr)
```


# Data

We will be using stock prices in this analysis. Although some of you know already how to use an API to retrieve stock prices I obtained the stock prices for every stock in the S&P 500 index for you already. The files are saved in the `session_6_data` directory. 

We can read in the stock prices. The data is 1.2M observations. The most important columns for our analysis are:

- `symbol`: The stock ticker symbol that corresponds to a company's stock price
- `date`: The timestamp relating the symbol to the share price at that point in time
- `adjusted`: The stock price, adjusted for any splits and dividends (we use this when analyzing stock data over long periods of time) 


```{r}
# STOCK PRICES
sp_500_prices_tbl <- read_rds("C:/Users/jorda/OneDrive/Dokumente/GitHub/ss23-bdml-danny-jordan/sp_500_prices_tbl.rds")
sp_500_prices_tbl
```

The second data frame contains information about the stocks the most important of which are:

- `company`: The company name
- `sector`: The sector that the company belongs to

```{r}
# SECTOR INFORMATION
sp_500_index_tbl <- read_rds("C:/Users/jorda/OneDrive/Dokumente/GitHub/ss23-bdml-danny-jordan/sp_500_index_tbl.rds")
sp_500_index_tbl
```

