---
title: "Supervised ML - Regression (I) & Supervised ML - Regression (II)"
author: "Danny Jordan"
---




#Load all neccessary libraries

```{r}
# Standard
library(tidyverse)

# Modeling
library(parsnip)

# Preprocessing & Sampling
library(recipes)
library(rsample)

# Modeling Error Metrics
library(yardstick)

# Plotting Decision Trees
library(rpart.plot)

library(rsample)
library(parsnip)
library(yardstick)
library(workflows)
```




# Load the 'bike_orderlines_tbl' data from the specified file
```{r}

bike_orderlines_tbl <- readRDS("C:/Users/jorda/OneDrive/Dokumente/GitHub/ss23-bdml-danny-jordan/bike_orderlines.rds")
bike_orderlines_tbl
# Display the structure of the 'bike_orderlines_tbl' data
glimpse(bike_orderlines_tbl)

#Create new table
model_sales_tbl <- bike_orderlines_tbl %>%

    #Select: total price, model, category_2 and frame material
    select(total_price, model, category_2, frame_material) %>%
    
    # Group the data by 'model', 'category_2', and 'frame_material'
    group_by(model, category_2, frame_material) %>%
    
    # Calculate the total sales for each combination of 'model', 'category_2', and 'frame_material'
    summarise(total_sales = sum(total_price)) %>%

    # Ungroup the data
    ungroup() %>%
   
    # Arrange the data in descending order of 'total_sales'
    arrange(desc(total_sales))

# Modify the 'category_2' column in 'model_sales_tbl' to reorder the levels based on 'total_sales'
model_sales_tbl %>%
    mutate(category_2 = as_factor(category_2) %>% 
               fct_reorder(total_sales, .fun = max) %>% 
               fct_rev()) %>%
  
    
    # Create a violin plot with 'frame_material' on the x-axis and 'total_sales' on the y-axis
    ggplot(aes(frame_material, total_sales)) +
    geom_violin() +  # Add violin plot
    geom_jitter(width = 0.1, alpha = 0.5, color = "#2c3e50") +  # Add jittered points
    facet_wrap(~ category_2) +  # Create separate facets for each 'category_2'
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M", accuracy = 0.1)) +  # Format y-axis labels as dollars in millions
    tidyquant::theme_tq() +  # Apply a theme from the tidyquant package
    labs(
        title = "Total Sales for Each Model",  # Set the title of the plot
        x = "Frame Material", y = "Revenue"  # Set the axis labels
    )


```


#Data Preparation
```{r}
bike_features_tbl <- readRDS("C:/Users/jorda/OneDrive/Dokumente/GitHub/ss23-bdml-danny-jordan/bike_features_tbl.rds")
glimpse(bike_features_tbl)
bike_features_tbl

bike_features_tbl <- bike_features_tbl %>% 
    select(model:url, `Rear Derailleur`, `Shift Lever`) %>% 
    mutate(
      `shimano dura-ace`        = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano dura-ace ") %>% as.numeric(),
      `shimano ultegra`         = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano ultegra ") %>% as.numeric(),
      `shimano 105`             = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano 105 ") %>% as.numeric(),
      `shimano tiagra`          = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano tiagra ") %>% as.numeric(),
      `Shimano sora`            = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano sora") %>% as.numeric(),
      `shimano deore`           = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano deore(?! xt)") %>% as.numeric(),
      `shimano slx`             = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano slx") %>% as.numeric(),
      `shimano grx`             = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano grx") %>% as.numeric(),
      `Shimano xt`              = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano deore xt |shimano xt ") %>% as.numeric(),
      `Shimano xtr`             = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano xtr") %>% as.numeric(),
      `Shimano saint`           = `Rear Derailleur` %>% str_to_lower() %>% str_detect("shimano saint") %>% as.numeric(),
      `SRAM red`                = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram red") %>% as.numeric(),
      `SRAM force`              = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram force") %>% as.numeric(),
      `SRAM rival`              = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram rival") %>% as.numeric(),
      `SRAM apex`               = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram apex") %>% as.numeric(),
      `SRAM xx1`                = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram xx1") %>% as.numeric(),
      `SRAM x01`                = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram x01|sram xo1") %>% as.numeric(),
      `SRAM gx`                 = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram gx") %>% as.numeric(),
      `SRAM nx`                 = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram nx") %>% as.numeric(),
      `SRAM sx`                 = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram sx") %>% as.numeric(),
      `SRAM sx`                 = `Rear Derailleur` %>% str_to_lower() %>% str_detect("sram sx") %>% as.numeric(),
      `Campagnolo potenza`      = `Rear Derailleur` %>% str_to_lower() %>% str_detect("campagnolo potenza") %>% as.numeric(),
      `Campagnolo super record` = `Rear Derailleur` %>% str_to_lower() %>% str_detect("campagnolo super record") %>% as.numeric(),
      `shimano nexus`           = `Shift Lever`     %>% str_to_lower() %>% str_detect("shimano nexus") %>% as.numeric(),
      `shimano alfine`          = `Shift Lever`     %>% str_to_lower() %>% str_detect("shimano alfine") %>% as.numeric()
    ) %>% 
  # Remove original columns  
  select(-c(`Rear Derailleur`, `Shift Lever`)) %>% 
  # Set all NAs to 0
  mutate_if(is.numeric, ~replace(., is.na(.), 0))

#bike_features_tbl
```


# Let’s order and tidy the tibble a bit. We need the following data:
```{r}
# 2.0 TRAINING & TEST SETS ----

bike_features_tbl <- bike_features_tbl %>% 
  
  mutate(id = row_number()) %>% 
  
  select(id, everything())
bike_features_tbl
```









# split data in test and train set (randomly)
```{r}
# Filter E-Road because it caused problems (just 1 element, and it could no be in training and test -> error bc not known)
bike_features_tbl <- bike_features_tbl %>%
  filter(category_2 != "E-Road")

bike_features_tbl %>% distinct(category_2)

sum(bike_features_tbl$category_2 == "E-Road")

# run both following commands at the same time
set.seed(seed = 1113)

split_obj <- initial_split(bike_features_tbl, prop = 0.80, strata = "category_2")

# Check if testing contains all category_2 values
split_obj %>% training() %>% distinct(category_2)
split_obj %>% testing() %>% distinct(category_2)

# Assign training and test data
train_tbl <- training(split_obj)
test_tbl  <- testing(split_obj)

# We have to remove spaces and dashes from the column names
train_tbl <- train_tbl %>% set_names(str_replace_all(names(train_tbl), " |-", "_"))
test_tbl  <- test_tbl  %>% set_names(str_replace_all(names(test_tbl),  " |-", "_"))
```



# Linear Regression Model and prediction (bad result due to not well choosen features)
```{r}


model_01_linear_lm_simple <- linear_reg(mode = "regression") %>%
    set_engine("lm") %>%
    fit(price ~ category_2 + frame_material, data = train_tbl)
test_tbl

model_01_linear_lm_simple %>%
    predict(new_data = test_tbl)%>%

    bind_cols(test_tbl %>% select(price)) %>%
  
    yardstick::metrics(truth = price, estimate = .pred)

```


# New Bike to predict price (use simpel model with bad prediction (since I had some issues with the engineered features)
```{r}

# 5.1 NEW MODEL ----

new_cross_country <- tibble(
        model = "Exceed AL SL new",
        category_2 = "Cross-Country",
        frame_material = "aluminium",
        shimano_dura_ace = 0,
        shimano_ultegra = 0,
        shimano_105 = 0,
        shimano_tiagra = 0,
        Shimano_sora = 0,
        shimano_deore = 0,
        shimano_slx = 0,
        shimano_grx = 0,
        Shimano_xt = 1,
        Shimano_xtr = 0,
        Shimano_saint = 0,
        SRAM_red = 0,
        SRAM_force = 0,
        SRAM_rival = 0,
        SRAM_apex = 0,
        SRAM_xx1 = 0,
        SRAM_x01 = 0,
        SRAM_gx = 0,
        SRAM_nx = 0,
        SRAM_sx = 0,
        Campagnolo_potenza = 0,
        Campagnolo_super_record = 0,
        shimano_nexus = 0,
        shimano_alfine = 0
) 

new_cross_country
predict(model_01_linear_lm_simple,, new_data = new_cross_country)
```


# engineered feature for better prediction
```{r}

# 3.2.1 Model ----
model_02_linear_lm_complex <- linear_reg("regression") %>%
    set_engine("lm") %>%
    
    # This is going to be different. Remove unnecessary columns.
    fit(price ~ ., data = train_tbl %>% select(-c(id:weight), -category_1, -c(category_3:gender)))

#model_02_linear_lm_complex %>% calc_metrics(new_data = test_tbl)

```












#1 CHALLENGE WITH RECIPES PACKAGE:
```{r}

# define the model
lm_model_spec <- linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")

```

#2
```{r}
recipe_obj <- recipe(price ~ ., data = train_tbl) %>%
  step_rm(id, url, model) %>%
  step_dummy(all_nominal(), -all_outcomes(), one_hot = TRUE) %>%
  prep()

# Apply preprocessing features to train and test data
train_transformed_tbl <- bake(recipe_obj, new_data = train_tbl)
test_transformed_tbl  <- bake(recipe_obj, new_data = test_tbl)

# Combine in workflow
workflow_obj <- workflow() %>%
  add_recipe(recipe_obj) %>%
  add_model(lm_model_spec) %>%
  fit(data = train_tbl)

# make predictions
predictions <- predict(workflow_obj, new_data = test_tbl)
```

```{r}

# Combine predictions with actual prices
predictions_with_actual <- bind_cols(test_transformed_tbl %>% select(price), predictions)

# Calculate evaluation metrics
evaluation_metrics <- yardstick::metrics(predictions_with_actual, truth = price, estimate = .pred)

# Print evaluation metrics
print(evaluation_metrics)

```
